Unified Understanding of the Dielectric Nature of Two-Dimensional Materials

### 2018-10-19 paper.tex
change slightly manuscript

$\varepsilon_{\mathrm{SL}}^{\perp}$, respectively (Figure \ref{fig-1}b
and \ref{fig-1}c insets). These findings indicate that the 2D
polarizability, instead of the dielectric constant, is the true
descriptor of the dielectric properties of 2D materials.

@@

(details see Supplementary Section SXX\todo{note}). We further prove,

@@

SXX\todo{note}), which we may relate with the thickness $\delta$ of

@@

Apart from the universal relations we propose for the 2D materials, it
is also of high theoretical interest to model the transition of
dielectric properties from the 2D world to the 3D world. In other
words, can we describe the dielectric constants of a bulk layered
material from the polarizabilities of the monolayer (see Figure
\ref{fig-4}a)? The static dielectric constants
$\varepsilon_{\mathrm{bulk}}$ for a bulk material with equilibrium
interlayer distance $L_{\mathrm{bulk}}$, can be expressed using the
polarizabilities of the individual layers in the bulk material
$\alpha_{\mathrm{bulk}}$:
\begin{eqnarray}
  \label{eq:3D-para}
  &\varepsilon^{\parallel}_{\mathrm{bulk}} &= 1 + {\displaystyle \frac{\alpha_{\mathrm{bulk}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{bulk}}}}\\
  \label{eq:3D-perp}
  &\varepsilon^{\perp}_{\mathrm{bulk}} &= \left(1 - \frac{\alpha_{\mathrm{bulk}}^{\perp}}{\varepsilon_{0} L_{\mathrm{bulk}}}\right)^{-1}
\end{eqnarray}
Note that $\alpha_{\mathrm{bulk}}$ may not essentially be the same as
$\alpha$ of isolated layer. Nevertheless we will first see how good
the predictions can be made when assuming
$\alpha_{\mathrm{bulk}}=\alpha$. Figure \ref{fig-4}b and \ref{fig-4}c
show the comparison between the
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ and
$\varepsilon_{\mathrm{bulk}}^{\perp}$ from first principles DFT
calculations compared with the values predicted using Eqs
\ref{eq:3D-para} and \ref{eq:3D-perp}, respectively. We observe that
such approach provides good estimation of
$\varepsilon_{\mathrm{bulk}}^{\parallel}$, with the mean average error
(MAE) of 1.35. On the other hand, we observe the predicted values of
$\varepsilon_{\mathrm{bulk}}^{\perp}$ has good agreement with the DFT
values when $E_{\mathrm{g}}>4$ eV, while the deviation becomes larger
when $E_{\mathrm{g}}$ reduces. Such results means that the
$\alpha^{\parallel}$ in a bulk layered material can generally be
estimated from its 2D counterpart, while $\alpha^{\perp}$ differs from
the values of monolayer, as also observed in other studies
\cite{Andersen_2015_dielec_vdWH,Laturia_2018}. Two factors contribute
to the discrepancy: (i) the overlap between induced dipoles is larger
perpendicular to the plane than parallel to the plane, and (ii) the
interlayer coupling is larger for 2D materials with smaller
bandgap. If we have an accuracy approach to model
$\alpha_{\mathrm{bulk}}$ as function of $\alpha$ and the degree of
interlayer coupling $\eta$ \cite{Tkatchenko_2012}, the dielectric
transition from 2D to 3D would be smoothly described.

Next we will show how the relation between dielectric properties
transforms from 2D to 3D. Extend the approach for modeling
$\alpha^{\parallel}$ in Eq. \ref{eq:alpha_perp_RPA} to the bulk
material, and use the Bloch presentation for wavefunctions in all
dimensions, we get:
\begin{equation}
  \label{eq:alpha-Eg-3D}
  \varepsilon_{\mathrm{bulk}} = 1 + \frac{2e^{2}}{\varepsilon_{0}(2\pi)^{3}}\int d^{3}\mathbf{k}
  \frac{|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(k)>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})}
\end{equation}
Using a similar treatment for
$|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(k)>|^{2}$ as in
Ref. \citenum{Jiang_2017_Eg_Eb} we end up with the relation
$\alpha_{\mathrm{bulk}} \propto 1/\sqrt{E_{\mathrm{g}}}$ (details see
Supplementary Section SXX \todo{note}), which recovers the Moss
relation under rigorous treatment \cite{Finkenrath_1988}. Therefore,
the universal $\alpha^{\perp}-E_{\mathrm{g}}$ relation is indeed the
Moss relation in 2D world, while the power law of $E_{\mathrm{g}}$ and
independence of effective mass is dominated by the confinement
perpendicular to the 2D plane.

Finally, we would like to comment on the generality of the dielectric
nature between the 2D and 3D worlds. As schematically shown in Figure
\ref{fig-2D-3D}, the physical quantities related to the dielectric
properties can be categorized into (i) strictly 2D (microscopic), (ii)
strictly 3D (macroscopic) and (iii) valid both 2D and 3D.  $\alpha$
and $\varepsilon$ are the starting point for the strictly 2D and 3D
quantities, which require distinct definitions when dimensionality
changes. Such quantities include (but not limited to):
\begin{enumerate}
\item The densities $n_{\mathrm{2D}}$ and $n_{\mathrm{3D}}$ for
  charge, polarization, electronic states, etc.

@@

To sum up, using first principles calculation for over 50 kinds of 2D
materials, we reveal the universal relation between the dielectric
nature of 2D materials and other physical quantities via the 2D
polarizability. The in-plane polarizability of a 2D material is found
to be inversely proportional to the minimal bandgap, while the
out-of-plane polarizability is the characteristic thickness of the 2D
material. Such universal scaling relation is explained by a quantum
mechanical model combining the polarizability in both directions. Our
universal scaling relation bridges the gap between 2D and 3D
dielectric properties with good accuracy of prediction.  Our numerical
findings and theoretical analysis pave the way to understand and
engineer the electronic and dielectric properties of a large library
of 2D materials for different technological applications in an
unified and unprecedented way.

@@

All results calculated for this paper were the result of \emph{ab
  initio} simulations carried out using plane-wave Density Functional
Theory (DFT) package VASP
\cite{Kresse_1993,Kresse_1996_1,Kresse_1996_2} using the Projector
Augmented Wave (PAW) approach with Kresse’s mainly GW
Pseudopotentials \cite{Kresse_1999_pseudopotentials}. Band gaps were
calculated using the Heyd-Scuseria-Ernzerhof hybrid functional (HSE06)
\cite{Heyd_2003,HSE_2006}, with Spin Orbit Coupling (SOC) explicitly
included. The geometries were converged both in cell parameters and
ionic positions, with forces below 0.04 eV/\AA. To ensure the accuracy
of dielectric property of monolayer, a vacuum spacing of $>$ 15 \AA is
used. A k-point grid of \(7\times7\times1\) was used to relax the
superlattice, with an initial relaxation carried out at the
Perdew-Burke-Ernzerhof
(PBE)\cite{Perdew_1996,Ernzerhof_1999,Paier_2005_PBE}
exchange-correlation functional level and a subsequent relaxation
carried out at HSE06 level, allowing both cell parameters and ionic
positions to relax each time. In VASP, the tag PREC=High was used,
giving a plane wave kinetic energy cutoff of 30\% greater than the
highest given in the pseudopotentials used in each material,
guaranteeing that absolute energies were converged to a few meV and
the stress tensor to within a few kBar.  Calculation of the
macroscopic ion-clamped dielectric tensor were carried out with an
18$\times$18$\times$1 k-grid and electric field strength of 0.001
eV/\AA. Bulk layered materials were constructed by relaxing the c-axis
length of corresponding monolayer material with the interlayer van der
Waals (vdW) interactions calculated by non-local vdW correlation
functional\cite{Lee_2010_vdFD2}. The dielectric properties of bulk
layered materials were calculated at PBE level with
18$\times$18$\times$6 k-grid with same parameter as for monolayer.

@@

% \section{Figures}
\label{sec:org34cbe74}
\begin{figure}[htbp]
\centering
\includegraphics[width=0.90\linewidth]{img/fig1.pdf}
\caption{\label{fig-1} The macroscopic dielectric constant and
  microscopic polarizability of a 2D material. \textbf{a}. Left: 2D
  material in a superlattice with length $L$ in the z-direction. The
  periodic images of the 2D material are shown below and above the
  superlattice. Right: simplied presentation of the dielectric
  constants $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
  $\varepsilon_{\mathrm{SL}}^{\perp}$ of the superlattice as a
  combined effect of the 2D polarizabilities $\alpha^{\parallel}$ and
  $\alpha^{\perp}$ and the vacuum. \textbf{b}. Change of spatial
  charge density $\Delta \rho(z)$ in the z-direction for a layer of
  2H-MoS$_{2}$ under external eletric field of 0.01 V/\AA{}. The green
  and red regions represent negative and positive induced charges,
  respectively. \textbf{c}. $\varepsilon^{\parallel}_{\mathrm{SL}}$
  (left) and $\alpha_{\mathrm{SL}}^{\parallel}$ (right) as functions
  of $L$ for a 2H-MoS$_{2}$
  layer. \textbf{d}. $\varepsilon^{\perp}_{\mathrm{SL}}$ (left) and
  $\alpha_{\mathrm{SL}}^{\perp}$ (right) as functions of $L$ for a
  2H-MoS$_{2}$ layer. The polarizabilities in \textbf{c} and
  \textbf{d} are constant when $L>$15 \AA{}.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\linewidth]{./img/fig2.pdf}
\caption{\label{fig-2} The 2D materials investigated. \textbf{a}. The
  elements that involved in this study. \textbf{b} 3D structures of
  the 2D materials investigated in this study.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.95\linewidth]{./img/fig3.pdf}
\caption{\label{fig-3} The universal scaling relation of the
  dielectric nature of 2D materials. \textbf{a}. $\alpha^{\parallel}$,
  $\alpha^{\perp}$ (bar plots) and $E_{\mathrm{g}}$ (blue dots) for
  all the 2D materials studied.  $\alpha^{\parallel}$ is observed to
  descend with increasing $E_{\mathrm{g}}$, while no apparent relation
  between $\alpha^{\perp}$ and $E_{\mathrm{g}}$ is
  observed. \textbf{b}. $(4\pi \varepsilon_{0})/\alpha^{\parallel}$
  (in \AA{}) as a function of $E_{\mathrm{g}}$, showing a linear
  correlation between each other. The energy range of visible light is
  shown in the
  background. \textbf{c}. $\alpha^{\perp}/(4\pi\varepsilon_{0})$ (in
  \AA{}) as a function of the covalent thickness, showing a perfect
  linear relation with slope very close to $1/4\pi$. The materials in
  \textbf{b} and \textbf{c} are grouped by their prototyes, including
  1T-TMDCs and cadmium halide (1T-MX$_{2}$), 2H-TMDCs (2H-MX$_{2}$),
  boron nitride (BN), phosphorene (P), monochalcogenides (GaS) and
  graphene derivatives (CH).}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{./img/fig4.pdf}
\caption{\label{fig-4} Transition of dielectric properties from 2D to
  3D systems. \textbf{a}. Scheme for the 2D-3D transition. $\alpha$ in
  the 2D material is essentially equivalent to $\varepsilon$ in its
  bulk counterpart. \textbf{b}
  $\varepsilon_{\mathrm{bulk}}^{\parallel}$ calculated from DFT
  (y-axis) compared with the predicted value from 2D
  $\alpha^{\parallel}$ (x-axis), showing good correlation. \textbf{c}
  $\varepsilon_{\mathrm{bulk}}^{\perp}$ calculated from DFT (y-axis)
  compared with the predicted value from 2D $\alpha^{\parallel}$
  (x-axis). The predicted value is in good aggreement with the DFT
  calculation when $E_{\mathrm{g}}>4$ eV, due to minimal interlayer
  coupling. }
\end{figure}

>>>>

$\varepsilon_{\mathrm{SL}}^{\perp}$, respectively (Figure \ref{fig-1}d
and \ref{fig-1}e). These findings indicate that the 2D polarizability,
instead of the dielectric constant, is the true descriptor of the
dielectric properties of 2D materials.

@@

(details see Supplementary Section S4). We further prove,

@@

S4), which we may relate with the thickness $\delta$ of

@@

Apart from the universal Moss-like relations we propose for the
dielectric nature of 2D materials, it is also of high theoretical
interest to model the 2D-3D transition of dielectric properties. In
other words, can we describe the dielectric constants
$\varepsilon^{\parallel}_{\mathrm{Bulk}}$ and
$\varepsilon^{\perp}_{\mathrm{Bulk}}$ of a bulk layered material from
$\alpha^{\parallel}$ and $\alpha^{\perp}$ of the monolayer (see Figure
\ref{fig-4}a)? First, we see that the 2D polarizabilities for
individual layers in the bulk materials
$\alpha_{\mathrm{Bulk}}^{\parallel}$ and
$\alpha_{\mathrm{Bulk}}^{\perp}$, can be calculated using
Eqs. \ref{eq:alpha-para-def} and \ref{eq:alpha-perp-def}, when $L$
becomes the bulk interlayer distance $L_{\mathrm{Bulk}}$. The
dielectric constants of the bulk material are then expressed as:
\begin{subequations}
\begin{eqnarray}
  \label{eq:3D-para}
  &\varepsilon^{\parallel}_{\mathrm{Bulk}} &= 1 + {\displaystyle \frac{\alpha_{\mathrm{bulk}}^{\parallel}}{\varepsilon_{0} L_{\mathrm{Bulk}}}}\\
  \label{eq:3D-perp}
  &\varepsilon^{\perp}_{\mathrm{Bulk}} &= \left(1 - \frac{\alpha_{\mathrm{Bulk}}^{\perp}}{\varepsilon_{0} L_{\mathrm{Bulk}}}\right)^{-1}
\end{eqnarray}
\end{subequations}
Note that $\alpha_{\mathrm{Bulk}}^{\parallel}$ and
$\alpha_{\mathrm{Bulk}}^{\perp}$ may not essentially be the same as
$\alpha$ of isolated layer, but still quite close as seen in Figure
\ref{fig-3}b and \ref{fig-3}c. Nevertheless we will first see how good
we can predict $\varepsilon_{\mathrm{Bulk}}^{\parallel}$ and
$\varepsilon_{\mathrm{Bulk}}^{\perp}$, when assuming
$\alpha_{\mathrm{bulk}}=\alpha$. We compare
$\varepsilon_{\mathrm{bulk}}^{\parallel}$ and
$\varepsilon_{\mathrm{bulk}}^{\perp}$ from first principles DFT
calculations compared with the values predicted using Eqs
\ref{eq:3D-para} and \ref{eq:3D-perp}, as show in Figure \ref{fig-4}b
and \ref{fig-4}c, respectively. Data calculated at both HSE06 and PBE
levels which give almost identical trends, indicating the generality
of such approach. Note although the stacking order is not considered
in Eqs. \ref{eq:3D-para} and \ref{eq:3D-perp}, we found that the
influence of stacking is minor (see Supplementary Figure SXX
\todo{Wait for Declan's data}). We observe that the majority of
predicted $\varepsilon_{\mathrm{bulk}}^{\parallel}$ values align along
the line $y=x$ , with a linear regression slope of 1.01 and $R^2$ of
0.97, indicating that such method indeed captures the transition from
$\alpha^{\parallel}$ to $\varepsilon_{\mathrm{Bulk}}^{\parallel}$. On
the other hand, we observe the predicted values of
$\varepsilon_{\mathrm{bulk}}^{\perp}$ has good agreement with the DFT
values when $E_{\mathrm{g}}>4$ eV, while the deviation becomes larger
when $E_{\mathrm{g}}$ reduces. The difference for the prediction of
$\varepsilon^{\parallel}$ and $\varepsilon^{\perp}$ means that
$\alpha^{\parallel}_{\mathrm{Bulk}}$ can generally be estimated from
its 2D counterpart, while $\alpha^{\perp}_{\mathrm{Bulk}}$ differs due
to interlayout coupling and overlap between induced dipoles, as also
observed in Figure \ref{fig-3}b, \ref{fig-3}c, and other studies
\cite{Andersen_2015_dielec_vdWH,Laturia_2018}. With a better model
describing $\alpha_{\mathrm{bulk}}^{\perp}$ as function of
$\alpha^{\perp}$ and the degree of interlayer coupling $\eta$
\cite{Tkatchenko_2012}, the dielectric transition from 2D to 3D would
be smoothly described.

As described in the previous section, the 2D Moss-like relation
between $\alpha^{\parallel}$ and $E_{g}$ is similar to the 3D Moss
relation between $\varepsilon$ and $E_{g}$, with a different power
law. Such difference in the power law can indeed be explained by
modern theory of dielectric properties.  Extend the approach
Eq. \ref{eq:alpha_perp_RPA} to the bulk material, and use the Bloch
presentation for wavefunctions in all dimensions, we derive (detailed
procedure see Supplementary Section S4):
\begin{equation}
  \label{eq:alpha-Eg-3D}
  \begin{aligned}[t]
  \varepsilon_{\mathrm{bulk}} &= 1 + \frac{2e^{2}}{\varepsilon_{0}(2\pi)^{3}}\int d^{3}\mathbf{k}
  \frac{|<u_{\mathrm{v}}(\mathbf{k})|\nabla|u_{\mathrm{v}}(k)>|^{2}}
  {E_{\mathrm{c}}(\mathbf{k}) - E_{\mathrm{v}}(\mathbf{k})} \\
  &\propto E_{g}^{-\frac{1}{2}},\ \mathrm{when}\ \varepsilon_{\mathrm{Bulk}} \gg 1
\end{aligned}
\end{equation}
which recovers the 3D Moss relation. Therefore, the universal
$\alpha^{\parallel}-E_{\mathrm{g}}$ relation is indeed the Moss relation
in 2D world, while the power law of $E_{\mathrm{g}}$ and independence
of effective mass is a result of the confinement perpendicular to the
2D plane.

\todo{First leave this part untouched}
Finally, we would like to comment on the generality of the dielectric
nature between the 2D and 3D worlds. As schematically shown in Figure
\ref{fig-2D-3D}, the physical quantities related to the dielectric
properties can be categorized into (i) strictly 2D (microscopic), (ii)
strictly 3D (macroscopic) and (iii) valid both 2D and 3D.  $\alpha$
and $\varepsilon$ are the starting point for the strictly 2D and 3D
quantities, which require distinct definitions when dimensionality
changes. Such quantities include (but not limited to):
\begin{enumerate}
\item The densities $n_{\mathrm{2D}}$ and $n_{\mathrm{3D}}$ for
  charge, polarization, electronic states, etc.

@@

To sum up, using first principles calculation for a large set of 2D
materials, we reveal the universal relation of the dielectric nature
of 2D materials using the 2D polarizability, as an analog to the Moss
relation for bulk semiconductors. The in-plane polarizability of a 2D
material is found to be inversely proportional to the minimal bandgap,
while the out-of-plane polarizability is the characteristic thickness
of the 2D material. Such universal scaling relation is explained by a
quantum mechanical model combining the polarizability in both
directions. Our universal scaling relation bridges the gap between 2D
and 3D dielectric properties with good accuracy of prediction.  Our
numerical findings and theoretical analysis pave the way to understand
and engineer the electronic and dielectric properties of a large
library of 2D materials for different technological applications in an
unified and unprecedented way.

@@

All results calculated for this paper were the result of \emph{ab
  initio} simulations carried out using plane-wave Density Functional
Theory (DFT) package VASP
\cite{Kresse_1993,Kresse_1996_1,Kresse_1996_2} using the Projector
Augmented Wave (PAW) approach with Kresse’s mainly GW
Pseudopotentials \cite{Kresse_1999_pseudopotentials}. Band gaps were
calculated using the Heyd-Scuseria-Ernzerhof hybrid functional (HSE06)
\cite{Heyd_2003,HSE_2006}, with Spin Orbit Coupling (SOC) explicitly
included. The geometries were converged both in cell parameters and
ionic positions, with forces below 0.04 eV/\AA. To ensure the accuracy
of dielectric property of monolayer, a vacuum spacing of $>$ 15 \AA is
used. A k-point grid of \(7\times7\times1\) was used to relax the
superlattice, with an initial relaxation carried out at the
Perdew-Burke-Ernzerhof
(PBE)\cite{Perdew_1996,Ernzerhof_1999,Paier_2005_PBE}
exchange-correlation functional level and a subsequent relaxation
carried out at HSE06 level, allowing both cell parameters and ionic
positions to relax each time. In VASP, the tag PREC=High was used,
giving a plane wave kinetic energy cutoff of 30\% greater than the
highest given in the pseudopotentials used in each material,
guaranteeing that absolute energies were converged to a few meV and
the stress tensor to within a few kBar.  Calculation of the
macroscopic ion-clamped dielectric tensor were carried out with an
18$\times$18$\times$1 k-grid and electric field strength of 0.001
eV/\AA. The materials in C2DB database for comparison were choses with
the GW bandgap larger than 0.05 eV. Bulk layered materials were
constructed by relaxing the c-axis length of corresponding monolayer
material with the interlayer van der Waals (vdW) interactions
calculated by non-local vdW correlation
functional\cite{Lee_2010_vdFD2}.  The dielectric properties of bulk
layered materials using VASP were calculated at HSE06 level with
18$\times$18$\times$6 k-grid with same parameter as for monolayer,
while the dielectric properties of bulk counterparts of the C2DB
database are calculated at PBE level with a k-point density of 10
\AA$^{-1}$.

@@

% \section{Figures}
\label{sec:org34cbe74}
\begin{figure}[htbp]
\centering
\includegraphics[width=0.75\linewidth]{img/fig1.pdf}
\caption{\label{fig-1} \textbf{2D polarizability as the true
    descriptor of the dielectric nature of 2D materials.}
  \textbf{a}. 3D illustration of the spatial distribution of the
  charge density change $\Delta \rho(z)$ along the z-direction for
  monolayer 2H-MoS$_{2}$ in a periodic superlattice under external
  eletric field of 0.01 V/\AA{}.  The green and red regions represent
  negative and positive induced charges, respectively. The macroscopic
  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
  $\varepsilon_{\mathrm{SL}}^{\perp}$ are influenced by the lattice
  size $L$, while the 2D polarizabilities $\alpha^{\parallel}$ and
  $\alpha^{\perp}$ are invariant with lattice size \textbf{b}.
  $\varepsilon^{\parallel}_{\mathrm{SL}}$ (top) and
  $\alpha_{\mathrm{SL}}^{\parallel}$ (bottom) as functions of $L$ for
  the 2H TMDCs. \textbf{c}.  $\varepsilon^{\perp}_{\mathrm{SL}}$ (top)
  and $\alpha_{\mathrm{SL}}^{\perp}$ (bottom) as functions of $L$ for
  the 2H TMDCs. The polarizabilities in \textbf{b} and \textbf{c} are
  constant when $L>$15 \AA{}, compared with the $L$-dependence of
  $\varepsilon_{\mathrm{SL}}$. \textbf{d} and \textbf{e}: modeled
  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
  $\varepsilon_{\mathrm{SL}}^{\perp}$ corresponding with \textbf{b}
  and \textbf{c}, from Eqs. \ref{eq:alpha-para-def} and
  \ref{eq:alpha-perp-def}, respectively.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.8\linewidth]{./img/fig2.pdf}
\caption{\label{fig-2} The elements and 3D structures of the 2D
  materials investigated in this study.}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=0.95\linewidth]{./img/fig3.pdf}
\caption{\label{fig-3} \textbf{The universal scaling relation of the
    dielectric nature of 2D
    materials}. \textbf{a}. $\alpha^{\parallel}$, $\alpha^{\perp}$
  (bar plots) and $E_{\mathrm{g}}$ (blue dots) for all the 2D
  materials studied.  $\alpha^{\parallel}$ is observed to descend with
  increasing $E_{\mathrm{g}}$, while no apparent relation between
  $\alpha^{\perp}$ and $E_{\mathrm{g}}$ is
  observed. \textbf{b}. $(4\pi \varepsilon_{0})/\alpha^{\parallel}$
  (in \AA{}$^{-1}$) as a function of $E_{\mathrm{g}}$, showing a linear
  correlation between each other. The energy range of visible light is
  shown in the
  background. \textbf{c}. $\alpha^{\perp}/(4\pi\varepsilon_{0})$ (in
  \AA{}) as a function of $\delta_{\mathrm{cov}}$ (definition
  schematically shown in the inset), showing a perfect linear relation
  with slope very close to $1/4\pi$. The universal scaling relation is
  also revealed using the C2DB database (squares), as superimposed on \textbf{b}
  and \textbf{c}.}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=\linewidth]{./img/fig4.pdf}
\caption{\label{fig-4} \textbf{Transition of dielectric properties
    from 2D to 3D systems}. \textbf{a}. Scheme for the 2D-3D
  transition. $\alpha$ in the 2D material is essentially equivalent to
  $\varepsilon$ in its bulk counterpart. \textbf{b}
  $\varepsilon_{\mathrm{bulk}}^{\parallel}$ calculated from DFT
  (y-axis) compared with the predicted value from 2D
  $\alpha^{\parallel}$ (x-axis), showing good correlation. \textbf{c}
  $\varepsilon_{\mathrm{bulk}}^{\perp}$ calculated from DFT (y-axis)
  compared with the predicted value from 2D $\alpha^{\parallel}$
  (x-axis). The predicted value is in good aggreement with the DFT
  calculation when $E_{\mathrm{g}}>4$ eV, due to minimal interlayer
  coupling. The comparisons in \textbf{b} and \textbf{c} are made
  based on both HSE06 (circles) and PBE (squares) levels.}
\end{figure}
